---
title: "p8105_hw6_as6447"
author: "Armaan Sodhi"
date: "2022-12-01"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)
library(modelr)
library(mgcv)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 10, 
  fig.height = 10,
  out.width = "90%")

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)


scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 2
Create a city_state variable (e.g. “Baltimore, MD”), and a binary variable indicating whether the homicide is solved. 

Omit cities Dallas, TX; 
Phoenix, AZ; and Kansas City, MO – these don’t report victim race. 
Also omit Tulsa, AL – this is a data entry mistake. 

For this problem, limit your analysis those for whom victim_race is white or black. 

Be sure that victim_age is numeric.
```{r}
homicide_data = read.csv('data/homicide-data.csv')%>%
   janitor::clean_names()%>%
   unite('city_state',city:state,remove=FALSE, sep = ', ')%>%
      unite('Victim_full_name',victim_first:victim_last,remove=FALSE, sep = ' ')%>%
   select(-city,-state,-victim_last,-victim_first)%>%
   rename(longitude=lon, latitude=lat)%>%
   mutate(
      unsolved_murder = if_else(disposition %in% c("Closed without arrest","Open/No arrest"),1, 0),
      victim_age=as.numeric(victim_age),   
      resolved = as.numeric(disposition == "Closed by arrest"))%>% filter(victim_race == 'Black'|victim_race=='White') %>% filter(!city_state %in% c('Phoenix, AZ','Kansas City, MO ','Tulsa, AL'))
 
```

For the city of Baltimore, MD, use the glm function to fit a logistic regression with 

resolved vs unresolved as the outcome and victim age, sex and race as predictors. 

Save the output of glm as an R object; apply the broom::tidy to this object; and 

obtain the estimate and confidence interval of the adjusted odds ratio for solving homicides comparing male victims to female victims keeping all other variables fixed.

```{r}
baltimore_df = 
  homicide_data%>% 
  filter(city_state == "Baltimore, MD") %>% 
  select(resolved, victim_age, victim_race, victim_sex)
```

```{r}
fit_logistic = 
  baltimore_df %>% 
  glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())
```

```{r}
fit_logistic %>% 
  broom::tidy() %>% 
  mutate(adjusted_OR = exp(estimate),
         lower_bound_CI = exp(estimate)-1.96*std.error,
         upperbound_CI = exp(estimate) +1.96*std.error
)%>%
  select(term, log_OR = estimate, adjusted_OR, lower_bound_CI,upperbound_CI,  p.value) %>% 
  knitr::kable()
```

Now run glm for each of the cities in your dataset, and extract the adjusted odds ratio (and CI) for solving homicides comparing male victims to female victims. 

Do this within a “tidy” pipeline, making use of purrr::map, list columns, and unnest as necessary to create a dataframe with estimated ORs and CIs for each city.

```{r}
fit_logistic_city = 
  homicide_data %>%
   nest(data=-city_state)%>%
   mutate(data,models=map(data, ~glm(resolved ~ victim_age + victim_race + victim_sex, data = ., family = binomial())),results = map(models, broom::tidy, conf.int = TRUE))%>%
   select(city_state,results)%>%
   unnest(cols = results)%>%
   filter(term != 'victim_sexUnknown')
```


Create a plot that shows the estimated ORs and CIs for each city. Organize cities according to estimated OR, and comment on the plot.
```{r}
fit_logistic_city%>% filter(
   term == 'victim_sexMale')%>%
   ggplot(aes(x=city_state,y=statistic,fill=fct_reorder(city_state,statistic,.desc = T ))) + geom_point() + geom_errorbar(aes(ymin = conf.low, ymax = conf.high )) + theme(axis.text.x = element_text(angle=90, hjust=1))
ggsave='data/homicide_map.pdf'
```


##Problem3


```{r}
birthweight_data = read.csv('data/birthweight.csv')%>%
   janitor::clean_names()%>%
   mutate(
      bwt=(bwt*0.00220462),
      babysex=  replace(babysex, babysex == 1 ,'Male'),
      babysex=  replace(babysex, babysex == 2 ,'Female'),
      frace=  replace(frace, frace == 1 ,'White'),
      frace=  replace(frace, frace == 2 ,'Black'),
      frace=  replace(frace, frace == 3 ,'Asian'),
      frace=  replace(frace, frace == 4 ,'Puerto Rican'),
      frace=  replace(frace, frace == 8 ,'Other'),
      frace=  replace(frace, frace == 9 ,'Unknown'),
      malform=  replace(malform, malform == 0 ,'Absent'),
      malform=  replace(malform, malform == 1 ,'Present'),
      mrace=  replace(mrace, mrace == 1 ,'White'),
      mrace=  replace(mrace, mrace == 2 ,'Black'),
      mrace=  replace(mrace, mrace == 3 ,'Asian'),
      mrace=  replace(mrace, mrace == 4 ,'Puerto Rican'),
      mrace=  replace(mrace, mrace == 8 ,'Other'),
      mheight = (mheight*2.54),
      fincome = (fincome*100)
   )
```
The data was loaded and tidied. Variables that were factors were converted from numeric. These were the fathers and mothers race, which were converted to the list the actual race/ethnicity rather than a numbered code. There was also unit conversions for height (inches) and weight (pounds) calculations . Income was converted to be in hundreds. 


Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. 

```{r}
birthweight_regression = 
  birthweight_data %>% 
  glm(bwt ~ momage, data = .)

birthweight_regression%>%broom::tidy()
```
Research has previously suggested that a mothers age can impact the birthwieght of the baby.


Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

```{r}
birthweight_data %>% 
  modelr::add_residuals(birthweight_regression) %>% 
   modelr::add_predictions(birthweight_regression)%>%
  ggplot(aes(x = momage, y = resid)) + geom_point()
```

Compare your model to two others:

One using length at birth and gestational age as predictors (main effects only)
```{r}
cv_df = 
  crossv_mc(birthweight_data, 100) 
```


```{r}
birthweight_models = 
  cv_df %>% 
   mutate(bwt_model_mine = map(train,~lm(bwt~momage,data=.x)),
   bwt_modelme_1 = map(data, ~lm(bwt~blength + gaweeks,data=.x)),
   bwt_modelme_2 = map(train, ~lm(bwt~bhead+blength+babysex+bhead*blength+bhead*babysex+babysex*blength+bhead*blength*babysex,data=.x)))%>%
      mutate(
         rmse_model = map2_dbl(btw_model_mine, test, ~rmse(model =.x,data=.y)),
         rmse_model1 = map2_dbl(bwt_modelme_1, test, ~rmse(model =.x,data=.y)),
         rmse_model2 = map2_dbl(bwt_modelme_2, test, ~rmse(model =.x,data=.y)))
   
```

One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
```{r}
birthweight_model2 = 
  birthweight_data %>% 
  glm(bwt ~ bhead*blength*babysex, data = .)%>% 
  broom::tidy() 
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}

```

