---
title: "p8105_hw6_as6447"
author: "Armaan Sodhi"
date: "2022-12-01"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(viridis)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 10, 
  fig.height = 10,
  out.width = "90%")

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)


scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d

theme_set(theme_minimal() + theme(legend.position = "bottom"))
```

## Problem 2

1.Describe the raw data. 

The raw data includes n=52179 observations with 12 variables. There are issues with some of the variable names, such as the `lon` variable, which is actually the longitudinal variable but is incorrectly stated. Another issue was that that the `city` and `state` are seperate from each other. These were instead combined together.

```{r}
homicide_data = read.csv('data/homicide-data.csv')%>% 
   janitor::clean_names()%>%
   unite('city_state',city:state,remove=FALSE, sep = ', ')%>%
      unite('Victim_full_name',victim_first:victim_last,remove=FALSE, sep = ' ')%>%
   select(-city,-state,-victim_last,-victim_first)%>%
   rename(longitude=lon, latitude=lat)%>%
   mutate(
      unsolved_murder = if_else(disposition %in% c("Closed without arrest","Open/No arrest"),1, 0),
       city_state = replace(city_state, city_state %in% 'Tulsa,AL','Tulsa,OK')
      )
  
```
`Baltimore_data` was created taking the homicide_data1 data, `filtering` for only `Baltimore,MD` and then using the `mutate` function to perform a proportional test using the `map2` function.
```{r}
baltimore_data= 
   homicide_data1%>%
   filter(city_state %in% 'Baltimore, MD')%>%
   mutate(p_test = 
             map2(number_unsolved_murders,total_number_homicides, ~prop.test(.x,.y )%>%
                     broom::tidy()))%>%unnest()%>%
   select(city_state,estimate,'CI_lower'=conf.low, 'CI_upper'=conf.high)
```

For the homicide cities section a similar function to the above was utilized, only this time without the `flter()`function.
```{r}
homicide_cities= 
   homicide_data1%>%
   mutate(p_test = map2(number_unsolved_murders,total_number_homicides,~prop.test(.x,.y)%>%broom::tidy()))%>%unnest()%>%
   select(city_state,estimate,'CI_lower' = conf.low, 'CI_upper' = conf.high)
```
